The Country-level Impact of Educational Patterns on the Rate of Entrepreneurship

### 2014-10-22 EducProposal.Rmd
Update EducProposal.Rmd

The key explanatory variable will be the degree of self confidence. As we did not find so far any satisfactory proxy for self-confidence in the way we intend to define it, we will need to compute an index. In order to do so, we will rely on both [OECD PISA](http://www.oecd.org/pisa/keyfindings/pisa-2012-results.htm), World Value Survey (Data from 2012 and 2005/2006 respectively) and GEM (Fear of failure rate, perceived capabilities).

V86   How important are adventure and taking risks to the person surveyed?  
V119 How good is competition?

Please note that data was collected at different dates in Britain (2005) and in France (2006), but in both cases before the economic crisis, which may have affected people’s prospects and values.

>>>>

The key explanatory variable will be the degree of self confidence. As we did not find so far any satisfactory proxy for self-confidence in the way we intend to define it, we will need to compute an index. In order to do so, we will rely on both [OECD PISA 2012](http://www.oecd.org/pisa/keyfindings/pisa-2012-results.htm), [World Value Survey 2005-2009](http://www.worldvaluessurvey.org/WVSOnline.jsp) and [GEM](http://www.gemconsortium.org)

From PISA 2012, we will use the items regarding engagement, drive and self-beliefs (Table III.2.3.a). More specifically we will compute data regarding the sense of belonging to measure the strength of inclusion in social networks. We also process measures of self-perception. They all come as a percentage of the country-representative student population.

From World Value Survey, we will use the last data available, that of the fifth wave (2005-2009). Our main issue is that data was collected at different points in time in Britain (2005) and in France (2006), but in both cases before the economic crisis, which might have affected people’s prospects and values differently. We will specifically look at the following items:
V86   How important are adventure and taking risks to the person surveyed?  
V119 How good is competition?

From GEM, we will use the most recent data available regarding the fear of failure rate and perceived capabilities).

To compute these data together is quite a challenge and we are not yet fully sure on how to proceed. But at least, these multiple reliable measures from well-recognised sources should give us a composite but also comprehensive indicator about the average degree of self-confidence of individuals in each country.
